A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-10 paper.tex
Add AES accelerator table

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{AES-NI}
    \caption{AES256 Encryption/Decryption Performance Numbers}
    \label{fig:AES-NI}
\end{figure}

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Fig.~\ref{fig:AES-NI} shows the performance of Encryption/Decryption of AES256 with and without hardware acceleration.

>>>>

\begin{table}[htbp]
	\caption{AES256 Encryption Performance Numbers}
	\label{tab:AES_NI}
	\begin{center}
        \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|  }
            %\hline
            %\multicolumn{4}{|c|}{} \\
            \hline
            Size& NON AES-NI (msecs) & AES-NI (msecs) & Encryption Acceleration (\%) \\
            \hline
            50 MB  & 1026  & 563   & 45.13 \\
            100 MB & 2036  & 1297  & 36.30 \\
            200 MB & 4282  & 2984  & 30.31 \\
            512 MB & 10754 & 6401  & 40.48 \\
            1 GB   & 23976 & 15721 & 34.43 \\
            \hline
        \end{tabular}
    \end{center}
\end{table}

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} According to Intel, Table~\ref{tab:AES_NI} shows the performance of Encryption of AES256 with and without hardware acceleration.
